Inferential Analysis of the \\ Supreme Court Citation Network

### 2018-01-04 Tex/presentations/SPSA2018/DesmaraisSPSATalk.tex
finished notation revisions

\frame{
\frametitle{The Exponential Random Graph Model (ERGM)}\vspace{0.5cm}

The probability (likelihood function) of observing network $N$ is:
\[
\mathcal{P}(N, \bt) = \frac{\exp \{ \bt' \bh(N)  \}}{\sum_{N^* \in \mathcal{N}} \exp \{\bt ' \bh(N^*)  \}}
\]
Decomposition:
\[
\underbrace{\bh(N)}_{Net\hspace{3pt} Stats} \qquad \underbrace{\bt}_{Effects} \qquad \underbrace{\exp \{\bt' \bh(N) \}}_{+ \hspace{3pt} Weight} \qquad \underbrace{\sum_{N^* \in \mathcal{N}} \exp \{\bt ' \bh(N^*)  \}}_{Normalizer}
\]

@@

>>>>

@@

\frame{
\frametitle{Citation Temporal Exponential Random Graph Model}\vspace{0.5cm}

The probability  of observing the $N_t \times N_{\leq t}$ adjacency matrix $C_t$ is
\[
\mathcal{P}(C_t, \bt) = \frac{\exp \{ \bt' \bh(C_{\leq t})  \}}{\sum_{C^*_t \in \mathcal{C}_t} \exp \{\bt ' \bh(C^*_{\leq t})\}  }
\]
Decomposition:
\[
\underbrace{\bh(C_{\leq t})}_{Net\hspace{3pt} Stats} \qquad \underbrace{\bt}_{Effects} \qquad \underbrace{\exp \{\bt' \bh(C_{\leq t}) \}}_{+ \hspace{3pt} Weight} \qquad \underbrace{\sum_{C^*_t \in \mathcal{C}_t} \exp \{\bt ' \bh(C^*_{\leq t})\}}_{Normalizer}
\]
